Baseline centering problem

### 2018-12-17 paper/tangotd.tex

Namely, set
\begin{equation}
A=\transp{\green}F, \qquad \green=\sum_s \green(s)\1_s,\qquad F=\E_{s\sim
\rho}
f(s)\1_s
\end{equation}
which is the same representation as above, namely $A=\Delta^{-1}$ is
equivalent to $\transp{\1_s}\green(s)\cdot \E_{s'\sim
\rho} \psi(s')f(s')=\transp{\1_s}\Delta^{-1}\psi$ for all $s$ and test
functions $\psi$.

>>>>

Namely, set
\begin{equation}
A=\transp{\green}F, \qquad \green=\sum_s \green(s)\transp{\1_s},\qquad F=\E_{s\sim
\rho}
f(s)\transp{\1_s}
\end{equation}
which is the same representation as above, namely $A=\Delta^{-1}$ is
equivalent to $\green(s)\cdot \E_{s'\sim
\rho} \psi(s')f(s')=\transp{\1_s}\Delta^{-1}\psi$ for all $s$ and test
functions $\psi$. Then the Newton equation for $A$ reads
\begin{equation}
\transp{\green}F\gets (1+\eta)\transp{\green}F-\eta \transp{\green}F \E_{ss'} \frac{1}{\rho(s)}\1_s\transp{(\1_s-\gamma
\1_{s'})} \transp{\green}F
\end{equation}
and since $F\1_s=\rho(s)f(s)$ and
$\transp{\1_s}\transp{\green}=\transp{\green(s)}$, this simplifies to
\begin{equation}
\transp{\green}F\gets (1+\eta)\transp{\green}F-\eta
\transp{\green} \E_{ss'} f(s)\transp{(\green(s)-\gamma
\green(s'))}F
\end{equation}
and we propose to update separately for $\green$ given $f$ and $f$ given
$\green$: the advantage being that for fixed $f$, we can obtain the
update above by updating $\green$ via
\begin{equation}
\transp{\green}\gets (1+\eta)\transp{\green}-\eta
\transp{\green} \E_{ss'} f(s)\transp{(\green(s)-\gamma
\green(s'))}
\end{equation}
and likewise for $f$ given $\green$,
\begin{equation}
F\gets (1+\eta)F-\eta
\E_{ss'} f(s)\transp{(\green(s)-\gamma
\green(s'))}F
\end{equation}
both of which can be implemented via gradient descent on the parameters
of $\green$ and $f$. There is no need to sample on test functions.
